\documentclass[11pt]{beamer}
\usepackage[utf8x]{inputenc}

\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{hyperref}

\usepackage{tikz}

\usetikzlibrary{arrows, backgrounds, positioning, fit, matrix}

\usepackage{gitdags}
\usepackage{color}
\usepackage{listings}

\input{theme/theme}

\newcommand\Small{\fontsize{8}{8.0}\selectfont}
\newcommand*\LSTfont{\Small\ttfamily}


\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{gray}{0.95}

\lstset{
    language=sh,
    basicstyle=\LSTfont,
    backgroundcolor=\color{mygray},
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    frame=single,
    rulecolor=\color{black},
    tabsize=4,
    breaklines=true,
    keywordstyle=\color{blue},
    commentstyle=\color{darkgray},
    stringstyle=\color{orange}
}

\date{11. Mai 2017}
\institute[ZIH TUD]{Zentrum f\"{u}r Informationsdienste und Hochleistungsrechnen -- TU Dresden}
\title[LCTP]{Introduction into Git}
\author[Oeste]{Sebastian~Oeste}

\room{FAL 245}
\address{Chemnitzer Strasse 46b}
\city{01069 Dresden}
\phone{+49 0351 - 463 32405}
\email{sebastian.oeste@tu-dresden.de}


\date{\today}

\setbeamercovered{transparent}

\begin{document}

\zihmaketitle



\begin{frame}[fragile]{I want to use git on my project, how do I start?}
    % TODO:
    % git config name/email
    % git init
\end{frame}

\begin{frame}[fragile]{There is this git Repository, how can I get it?}
    % TODO:
    % git clone
    % git clone -b
\end{frame}

\begin{frame}[fragile]{I made my changes, how do I review them?}
    % TODO:
    % git status
    % git diff
    % git log
\end{frame}

\begin{frame}[fragile]{My changes are looking good, and now?}
    % TODO:
    % git (un)staging
    % git commit
\end{frame}

\begin{frame}[fragile]{I messed-up the last commit, can I change it?}
    % TODO:
    % git commit --amend
\end{frame}

\begin{frame}[fragile]{I've made my commit, am I fine now?}
    % TODO:
    % git remotes?
    % git push
\end{frame}

\begin{frame}[fragile]{My push was rejected because of conflicts, what can I do?}
    % TODO:
    % git feature branch
\end{frame}

\begin{frame}[fragile]{How do I get updates?}
    % TODO:
    % git pull
    % git fetch?
\end{frame}

\begin{frame}[fragile]{How do I apply the updates to my branch?}
    % TODO:
    % git merge
    % git rebase
\end{frame}

\begin{frame}[fragile]{I just fixed this error, can I change the earlier commit?}
    % TODO:
    % git rebase -i
\end{frame}

\begin{frame}[fragile]{Help, I think I messed up!}
    % TODO:
    % git reflog
\end{frame}

\begin{frame}[fragile]{This git commands are too complicated to remember, are there easier ones?}
    % TODO:
    % gst
    % grb grbi grba grbc
    % gp gl
    % glog gloga
    % gco gcm
\end{frame}

\end{document}
